\documentclass{article}
%\usepackage[margin=2cm]{geometry}
\usepackage{tabularx}
\usepackage{fullpage}
\RequirePackage{fancyhdr}

\begin{document}

\section*{Courseflow Survey}

\vspace{0.5cm}

Thank you for participating in our demonstration of CourseFlow. Please consider answering the following questions about your experience with CourseFlow to help us develop it to better suit your needs.

\subsection*{Quick Questions:}

\textbf{Rate CourseFlow on a scale of 1-5 in the following areas:}

{\small \textbf{(1 -- Strongly disagree, 2 -- Disagree, 3 -- Neutral/unsure, 4 -- Agree, 5 -- Strongly agree)}}

\begin{enumerate}
\item Usefulness: The program is useful to me.

\begin{tabularx}{0.5\textwidth}{XXXXXX}
&1&2&3&4&5
\end{tabularx}
\item Pedagogy: The program encourages me to improve my pedagogy and/or use active learning.

\begin{tabularx}{0.5\textwidth}{XXXXXX}
&1&2&3&4&5
\end{tabularx}
\item Visualization: The program's visualizations give me useful insight into the pedagogy I use.

\begin{tabularx}{0.5\textwidth}{XXXXXX}
&1&2&3&4&5
\end{tabularx}
\item Flexibility/Customization: The program is flexible enough for me to use it the way I want.

\begin{tabularx}{0.5\textwidth}{XXXXXX}
&1&2&3&4&5
\end{tabularx}
\item Ease of use: The program is intuitive and easy to use.

\begin{tabularx}{0.5\textwidth}{XXXXXX}
&1&2&3&4&5
\end{tabularx}

\item Interface: The program looks well designed and professional.

\begin{tabularx}{0.5\textwidth}{XXXXXX}
&1&2&3&4&5
\end{tabularx}

\end{enumerate}

\subsection*{Detailed Questions:}



\begin{enumerate}
\item \textbf{What features did you like about Courseflow?}

\begin{tabularx}{0.9\textwidth}{X}
\\
\hline
\\
\hline
\\
\hline
\\
\hline
\end{tabularx}

\item \textbf{What features did you dislike about Courseflow?}

\begin{tabularx}{0.9\textwidth}{X}
\\
\hline
\\
\hline
\\
\hline
\\
\hline
\end{tabularx}

\item \textbf{What features is Courseflow missing?}

\begin{tabularx}{0.9\textwidth}{X}
\\
\hline
\\
\hline
\\
\hline
\\
\hline
\end{tabularx}

\clearpage

\item \textbf{Which best describes your role in education? (select multiple if applicable)}
\begin{enumerate}
\item Instructor (day classes)
\item Instructor (cont. ed.)
\item Education researcher
\item Curriculum/program developer/designer
\item Other: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}
\end{enumerate}


\item \textbf{How likely are you to use CourseFlow?}
\begin{enumerate}
\item Very likely
\item Likely
\item Neutral/unsure
\item Unlikely
\item Very unlikely
\end{enumerate}

\item \textbf{For what purpose would you most likely use CourseFlow?  (select multiple if applicable)}
\begin{enumerate}
\item Planning my class activities
\item Planning my courses
\item Sharing courses/activities with colleagues
\item Sharing courses/activities with researchers
\item Program development/curriculum design
\item Tracking outcomes in a course
\item Tracking outcomes in a program
\item Given to students as an interactive course outline
\item Other: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}
\end{enumerate}

\item \textbf{What single feature or change would most make you more likely to use CourseFlow?}

\begin{tabularx}{0.9\textwidth}{X}
\\
\hline
\\
\hline
\\
\hline
\\
\hline
\end{tabularx}

\item \textbf{Other comments:}

\begin{tabularx}{0.9\textwidth}{X}
\\
\hline
\\
\hline
\\
\hline
\\
\hline
\\
\hline
\\
\hline
\end{tabularx}

\item If you are willing to be contacted for further inquiries or details about your feedback, you may write your name and email below. \textbf{If you prefer to remain anonymous, leave this blank.}

Name: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}
Email: \underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}

\end{enumerate}

\end{document}